---
title: "H10"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r data}
cancer <- read.csv("breast-cancer-wisconsin.data.txt",header=F,na.strings = '?')
head(df)
```
```{r na}
#  NA/missing values 
sum(is.na.data.frame(cancer))
```
```{r pattern}
#install.packages("mice")
library('mice')
md.pattern(cancer,plot = TRUE, rotate.names = FALSE)
```
#Multivariate Imputation by Chained Equations (MICE) package can be used to produce a table displaying the missing pattern . “1” indicates nonmissing value and “0” indicates missing value.
```{r ma}
#install.packages("naniar")
library(naniar)
vis_miss(cancer)
```
# variable V7 has missing values
```{r imp}
# Imputation
tempData <- mice(cancer,m=5,maxit=50,meth='pmm',seed=500)
summary(tempData)
densityplot(tempData)
```

```{r vector}
#impute using mean
na_v = as.vector(cancer$V7)
na = mean(na_v, na.rm = TRUE)
mean_fn <- function(na_v) replace(na_v, is.na(na_v), mean(na_v, na.rm = T))
# apply functioned defined above to impute missing values with mean of the colum
df_mean <- as.data.frame(lapply(cancer, mean_fn))
#number of missing values
sum(is.na.data.frame(df_mean))
```

```{r regression}
na_reg <-mice(cancer,method = 'norm.predict')
df_regression <- complete(na_reg)
#number of missing values 
sum(is.na.data.frame(df_regression))
```
```{r plot1}
densityplot(na_reg)
```
#The density of the imputed data for each imputed dataset is showed in red while the density of the observed data is showed in blue. as expected the distributions are similar.

```{r pert}
df_pert<-mice(cancer,method = 'norm.nob')
df_perturb <- complete(df_pert)
#number of missing values 
sum(is.na.data.frame(df_perturb))
```
```{r plot2}
densityplot(df_pert)

```

#The density of the imputed data for each imputed dataset is showed in red while the density of the observed data is showed in blue. as expected the distributions are similar.





















































































